The Constant-Q Transform Spectral Envelope Coefficients: a musically-adapted timbre feature

### 2021-05-13 IEEE SP Magazine/05-2021 - Draft/article.tex
Started writing intro in draft.

\title{The Constant-Q Transform \\ Spectral Envelope Coefficients}

@@

\section{Scope}

\IEEEPARstart{T}{he} sliding discrete Fourier transform (SDFT) ...

%One paragraph describing the article content

\cite{brown1991}, \cite{brown1992}

\cite{engel2017}: NSynth

- Aware that some methods are attempting to learn more adapted feature like that 
- The envelope component can additionally be refined, along with the pitch component
- Incidentally, the pitch component can be used to identify the pitch/key

\section{Relevance}

%one or two paragraphs

@@

@@

@@

\section{Numerical Example}

% or "V - Computational Example"

\section{What We Have Learned}

@@

% One paragraph

>>>>

\title{The Constant-Q Transform Spectral Envelope Coefficients: a musically-adapted timbre feature}

@@

\section{Scope}
%One paragraph describing the article content

%- Aware that some methods are attempting to learn more adapted feature like that 
%- The envelope component can additionally be refined, along with the pitch component
%- Incidentally, the pitch component can be used to identify the pitch/key

% We are presenting a timbre feature better suited to musical data
% We will show how to derive it from the CQT, by decomposing it into a pitch-invariant spectral envelop and a normalized pitch component
% We will show how it compares to the MFCC, commonly-used as the timbre feature, on the NSynth dataset

\IEEEPARstart{T}{imbre} is the attribute of sound which makes, for example, two musical instruments playing the same note sound different. It is generally associated with the spectral (but also temporal) envelope and is typically assumed to be independent from the pitch (but also the loudness) of the sound \cite{moore2004}. This article will show how to derive a simple but ... timbre feature ...

\cite{brown1991}, \cite{brown1992}
\cite{engel2017}: NSynth

\section{Relevance}
%One or two paragraphs

% A good pitch-invariant timbre feature can help for identifying musical instruments 
% Additionally, we will show how to decompose the CQT spectrum into a pitch-invariant envelope and a normalized pitch component, which can be reused

@@

% There is no proper timbre feature, especially for music data.
% People use MFCC, originally designed for speech data, other tried to learn such features
%

@@

\section{Numerical Example}
% or "V - Computational Example"

@@

\section{What We Have Learned}
% One paragraph

@@
